---
title: "palettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{palettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(jonohey)
```


```{r}
# show_col
jonohey_show("autumn")

```

```{r}
jonohey_show("flying_fabric")
```

Here are all palettes

```{r}
invisible(lapply(jonohey_palettes(), jonohey_show))
```



```{r}
# discrete
library(ggplot2)
ggplot(mtcars, aes(factor(cyl), mpg, fill = factor(cyl))) +
  geom_boxplot() +
  scale_fill_jonohey("suit")

```


```{r}
# continuous example
# DEMO ONLY
# Probably not the best color choice!!!!
ggplot(faithfuld, aes(eruptions, waiting, fill = density)) +
  geom_raster() +
  scale_fill_jonohey("surfing", discrete = FALSE)
```


## Using the theme

We provide two different themes:

* `theme_card()` will give you a nice round edge around the plot panel or/and plot background

```{r}
p <- ggplot(mtcars, aes(factor(cyl), mpg, fill = factor(cyl))) +
  geom_boxplot(width = 0.7) +
  scale_fill_jonohey("suit")

# round panels
p + theme_card()
```

To better understand the functioning of this theme, here are some examples:

```{r}
# Rounded panel only
# same fill for plot bg
p + theme_card(radius_panel = 50)
# to show the different elements
p + theme_card(radius_panel = 50, plot_bg_fill = "gray50")
# Rounded plot background and rounded panel
p + theme_card(radius_panel = 30, round_plot = TRUE, radius_plot = 70,
               plot_bg_fill = "gray50")
# Transparent outer card, rounded inner panel
p + theme_card(radius_panel = 30, round_plot = FALSE, plot_bg_fill = NA)
```


* `theme_jonohey_wiggle()` will give you wiggly axis. 

```{r}
p + theme_axes_wiggle()
```

As of this version, we provide minimal wiggly configurations powered by `{elementalist}`[]. If you decide you need more grooves you can implement it yourself. For example:

```{r}
 p +
  theme_axes_wiggle() + 
  theme(panel.grid.major = elementalist::element_line_wiggle(3, 
                                                             color = "gray20",
                                                             linewidth = 0.2))
```

