---
title: "Basic Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basic-usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Palettes

At its core, `{jonohey}` is about color palettes. You can display the palettes using the helper function `jonohey_show()`

```{r setup}
library(jonohey)
# show_col
jonohey_show("autumn")

```

Here's another example:

```{r}
jonohey_show("flying_fabric")
```

### All palettes

Here are all available palettes by name.

```{r}
jonohey_palettes()
```


> Notice that as of this version, we store two single colors in palettes for convenience. One of them is the background for the theme. The other one is the ba. It's likely that these colors will be internalized in the future 

Take a look at all palettes in full color :)

```{r}
invisible(lapply(jonohey_palettes(), jonohey_show))
```

## Applying palettes

We provide `scale_fill_jonohey()` and `scale_color_jonohey()` to be able to integrate this package into `ggplot2`. Here's an example

```{r}
# discrete
library(ggplot2)
ggplot(mtcars, aes(factor(cyl), mpg, fill = factor(cyl))) +
  geom_boxplot() +
  scale_fill_jonohey("suit")

```

In principle, one could use these palettes for continuous mapping too. You are advised against doing so, but nobody is really stopping you right now.


```{r}
# continuous example
# DEMO ONLY
# Probably not the best color choice!!!!
ggplot(faithfuld, aes(eruptions, waiting, fill = density)) +
  geom_raster() +
  scale_fill_jonohey("surfing", discrete = FALSE)
```


## Using the theme

We provide two different themes:

* `theme_card()` will give you a nice round edge around the plot panel or/and plot background

```{r}
p <- ggplot(mtcars, aes(factor(cyl), mpg, fill = factor(cyl))) +
  geom_boxplot(width = 0.7) +
  scale_fill_jonohey("suit")

# round panel and plot
p + theme_card(round_plot = TRUE, radius_plot = 50)
```

To better understand the functioning of this theme, here are some examples:

```{r}
# Rounded panel only
p + theme_card(radius_panel = 20)
# plot not rounded, fill with gray50
p + theme_card(radius_panel = 20, plot_bg_fill = "gray50")
# Rounded plot background and rounded panel
# increased rounding for both
p + theme_card(radius_panel = 30, round_plot = TRUE, radius_plot = 70,
               plot_bg_fill = "gray50")
# Transparent outer card, rounded inner panel
p + theme_card(radius_panel = 30, round_plot = FALSE, plot_bg_fill = NA)
```


* `theme_jonohey_wiggle()` will give you wiggly axis. 

```{r}
p + theme_axes_wiggle()
```

As of this version, we provide minimal wiggly configurations powered by [`{elementalist}`](https://teunbrand.github.io/elementalist/index.html). If you decide you need more grooves you can implement it yourself. 

For example:

```{r}
 p +
  theme_axes_wiggle() + 
  theme(panel.grid.major = elementalist::element_line_wiggle(2, 
                                                             color = "gray20",
                                                             linewidth = 0.2))
```

